\documentclass{resume}
\usepackage{fontawesome}
\usepackage{tikz,xcolor,hyperref}

\definecolor{lime}{HTML}{A6CE39}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{0.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{\href{https://linkedin.com/in/arootinghn}{Arootin Gharibian}}
\DeclareRobustCommand{\orcidicon}{
	\begin{tikzpicture}
	\draw[lime, fill=lime] (0,0) 
	circle [radius=0.16] 
	node[white] {{\fontfamily{qag}\selectfont \tiny ID}};
	\draw[white, fill=white] (-0.0625,0.095) 
	circle [radius=0.00];
	\end{tikzpicture}
	\hspace{2mm}
}
\address{Yerevan, Armenia \\ (374)95259522 }
\address{\href{mailto:arootin.gharibyan@gmail.com}{arootin.gharibyan@gmail.com}}
\begin{document}
\begin{rSection}{Education}
{\href{https://science.ut.ac.ir/en/web/biology}{University of Tehran}}\hfill\href{https://orcid.org/0000-0001-7819-0842}{\orcidicon}\\
{\bf Master of Science; Biology, Cellular and Molecular Sciences} \hfill {Sep. 2011 -- Sep. 2014}\\
 Thesis Title: A study on the role of LTBP-1 in human trabecular meshwork cells \hfill {\textit{CGPA} : \textsl{87 \%}}\\
 
{\bf Bachelor of Science; Biology, Cellular and Molecular Sciences} \hfill {Sep. 2006 - Sep. 2010}\\
 Thesis Title: Genetic delimitation of \href{https://onlinelibrary.wiley.com/doi/abs/10.1111/boj.12015}{\textit{Amaranthaceae and Chenopodiaceae}} populations \hfill {\textit{CGPA} : \textsl{80 \%}}
\end{rSection}

\begin{rSection}{SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l}

Regulatory Skills & European Medical device regulations (MDR \& IVDR), Technical documentation.\\
Research Skills & Genomics, Flow cytometry, Data analysis, Clinical research, Literature review.\\
Tools \& Frameworks & R-studio, Jupyter, Virtualization, Scripting.\\
Languages & R for Statistical programming, Python.
\end{tabular}\\
\end{rSection}


\begin{rSection}{Work History}
\vspace{-1.25em}
\item \textbf{Regulatory Affairs Team Lead,} Medical Devices \hfill May 2020 - Present\\
\href{https://clinchoice.com/contact/}{ClinChoice LLC} \hfill Yerevan, Armenia
\item \textbf{Application Sales and Scientific Marketing Specialist,} IVD devices \hfill Oct. 2017 - Apr. 2020\\
\href{https://www.sysmex-europe.com/products/diagnostics/haematology.html}{Electronic Pezeshki Pishrafteh} \hfill Tehran, Iran
\item \textbf{Biology Teacher}, Part time, Contract\hfill Jul. 2007 - Jun. 2017\\
\href{https://en.wikipedia.org/wiki/National_Organization_for_Development_of_Exceptional_Talents}{National Organization for Development of Exceptional Talents} \hfill Tehran, Iran
\end{rSection}

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{MDR Transition Technical Documentation Publishing} \hfill \href{https://clinchoice.com/solutions/medical-device-regulatory-affairs/technical-document-submission-approval-preparation/}{ClinChoice LLC}
\begin{itemize}
    \itemsep -3pt {} 
     \item Authoring of Summary technical documentation (TD) for submission for EU MDR certification.
     \item Compilation of documentation required for medical device submission in European Economic Area.
     \item Submitted more than 50 medical device TDs, including combinations and biologics.
 \end{itemize}

\item \textbf{Application Sales and Scientific Marketing} \hfill {\href{https://www.sysmex-europe.com/products/diagnostics/haemostasis.html}{Electronic Pezeshki Pishrafteh}}
\begin{itemize}
    \itemsep -3pt {} 
     \item Application specialist for haemostasis and haematology IVD Devices.
     \item Scientific marketing and training end users.
     \item Post-market quality review, sales trend analysis.
     \item Support laboratories in optimization of testing portfolio.
 \end{itemize}
\item \textbf{Research Associate} \hfill \href{http://www.nigeb.ac.ir/web/en}{National Institute of Genetic Engineering and Biotechnology}
\begin{itemize}
    \itemsep -3pt {} 
     \item Topic: Early Detection of Breast Cancer using plasma cfDNA methylation pattern.
     \item Grant proposal writing, data analysis.
 \end{itemize}
\end{rSection} 


% ----------------------------
% \begin{rSection}{EXPERIENCE}

% \textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
% Company Name \hfill \textit{San Francisco, CA}
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Achieved X\% growth for XYZ using A, B, and C skills.
%      \item Led XYZ which led to X\% of improvement in ABC
%     \item Developed XYZ that did A, B, and C using X, Y, and Z. 
%  \end{itemize}
% \textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
% Company Name \hfill \textit{San Francisco, CA}
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Achieved X\% growth for XYZ using A, B, and C skills.
%      \item Led XYZ which led to X\% of improvement in ABC
%     \item Developed XYZ that did A, B, and C using X, Y, and Z. 
%  \end{itemize}

% \end{rSection} 
%--------------------------------------------------------------------------------

\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
   \item 	Birthright Armenia Volunteer program, \hfill Dec. 2019\\
   Institute of Molecular Biology, BioInformatics Group.\hfill Yerevan, Armenia.
   \end{itemize}
\end{rSection}


\end{document}
