\documentclass{resume}
\usepackage{fontawesome5}
\usepackage{tikz,xcolor,hyperref}
\usepackage{marvosym}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{mwe}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry}
\definecolor{lime}{HTML}{A6CE39}
\DeclareRobustCommand{\orcidicon}{
	\begin{tikzpicture}
	\draw[lime, fill=lime] (0,0) 
	circle [radius=0.15] 
	node[white] {{\fontfamily{qag}\selectfont \tiny iD}};
	\draw[white, fill=white] (-0.0625,0.095)
	circle [radius=0.00];
	\end{tikzpicture}
	\hspace{1mm}}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    pdftitle={CV-A-Gharibian-2024},
    bookmarksopen=false,
    pdfauthor= Arootin Gharibian
}

\newcommand{\tab}[1]{\hspace{0.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Arootin Gharibian}
\address{Czech Republic}
\begin{document}
\begin{rSection}{SKILLS}
\vspace{-0.11em}
\setstretch{1.25}
\begin{tabular}{@{} >{\bfseries}l @{\hspace{8ex}} l}
Industry Skills & Regulatory Affairs, Scientific Marketing, In-Vitro Diagnostics.\\
Research Skills & Clinical Research and Data Analysis, Systematic Reviews.\\
Regulatory Knowledge & EU-MDR \& EU-IVDR, QMS, ISMS, Risk Management.\\
Domain Knowledge & Flow-Cytometry, Genomics and Molecular Biology.\\
Tools \& Frameworks & DMS, Data Mining \& Data Visualization.\\

\end{tabular}
\end{rSection}

\begin{rSection}{Recent Work History}
\vspace{-1em}
\setstretch{1.25}
\item \textbf{Researcher, Computational Biology}\\
\href{https://www.fei.vsb.cz/en/research/research-groups/?id=19}{V\v{S}B - Technical University of Ostrava}{\href{https://orcid.org/0000-0001-7819-0842}{\orcidicon}} \hfill (Full time) January 2023 - December 2024\\
\textit{Ostrava, Czech Republic}\\
\href{https://www.fnol.cz/en/o-nas}{Olomouc University Hospital}\hfill (Part time) January 2022 - December 2023\\
\textit{Olomouc, Czech Republic}

\item \textbf{Medical Writer, Pharmacovigilance} \hfill (Full time) August 2022 - December 2022\\
\textbf{Regulatory Affairs Team Lead, MDR} \hfill (Full time) May 2020 - August 2022\\
\href{https://clinchoice.com/about}{ClinChoice LLC.}

\end{rSection}

\begin{rSection}{WORK EXPERIENCE}
\vspace{-1em}
\setstretch{1.11}
\item \textbf{Regulatory Affairs Team Lead, MDR} \hfill {ClinChoice LLC}
\begin{itemize}
    \itemsep -2.25pt {}
    \item Coordinated Technical Documentation compilation for MDR re-certification:\hfill {\tiny{\href{https://clinchoice.com/solutions/medical-device-regulatory-affairs/technical-document-submission-approval-preparation}{\faIcon{external-link-alt}}}}\\
          50 Class II \& III medical devices, and 3 drug-device combination products.
    \item Established control processes for continuous compliance of TDs with respect to EU-MDR.
    \item Authored standard procedures, training material and risk management plans (\textsc{ISO-13485}).
\end{itemize}

\item \textbf{Medical Writer, Pharmacovigilance}
\begin{itemize}
    \itemsep -2.25pt {}
    \item Prepared ad-hoc systematic reviews for submission to regulatory authorities. \hfill {\tiny {\href{https://clinchoice.com/solutions/medical-device-safety/literature-monitoring/}{\faIcon
{external-link-alt}}}}
    \item Developed high-level search strategy with surveillance physician and medical librarians. 
    \item Performed routine literature searches and identified/analysed relevant publications.\\
\end{itemize}

\item \textbf{Application Sales and Scientific Marketing} \hfill {Electronic Pezeshki Pishrafteh Co. Ltd.}
\begin{itemize}
    \itemsep -2.25pt {} 
    \item Executed scientific marketing activities for haemostasis and haematology devices.\hfill {\tiny \href{https://www.sysmex-europe.com/company/contacts/distributors.html}{\faIcon{external-link-alt}}}
    \item Coordinated with RA and QA departments for continuous availability of critical centres.
    \item Supported customer process adaptation and methodology transition for \textsc{ISO-15189} compliance.
    \item Executed training activities for end-users and internal field service engineers.
    \item Mediated post-market surveillance for more than 2000 devices.
\end{itemize}

\end{rSection}
     \newpage


\begin{rSection}{Research Experience}
\vspace{-1em}
\setstretch{1.25}
\item {V\v{S}B - Technical University of Ostrava}
    \begin{itemize}
        \itemsep -2.22pt {}
                 \item Implementing new ML-based algorithms for semi-supervised FCS dataset exploratory analysis.
                 \item Implementing new algorithms for community analysis of migratory cells \textit{in-vitro}.
    \end{itemize}
\item {Olomouc University Hospital} \hfill {\tiny \href{http://olgen.cz/en/team-members}{\faIcon{external-link-alt}}}


    \begin{itemize}
        \item Implemented \href{https://doi.org/10.1007/978-3-031-40971-4_41}{Clinical Data Analysis pipeline for exploratory data mining}.
        \itemsep -2.22pt {}
            \subitem $\cdot$ Visual data-flow management for continuous import of real-world clinical datasets.
            \subitem $\cdot$ Iterative data imputation and processing for handling missing and incomplete data.
            \subitem $\cdot$ Graph-based visualization of data for patient similarity networks identifying risk groups.
    \end{itemize}
\end{rSection}

\begin{rSection}{Education}

\setstretch{1.25}
\textbf{Bioinformatics and Computational Biology} \hfill{V\v{S}B - Technical University of Ostrava}\\
{\bf PhD student;} \hfill {September 2021 -- August 2025 (expected)}\\
Thesis Topic: Multi-Modal Real-World Clinical Data Mining. \hfill {\tiny{{\href{https://www.vsb.cz/en/study/degree-students/degree-studies/doctoral-degree/doctoral-degree-detail/?programmeId=836}{\faIcon{external-link-alt}}}}}

\textbf{Cellular and Molecular Biology} \hfill{\tiny{{\href{https://science.ut.ac.ir/en/web/biology/cell-mol-biology}{\faIcon
{external-link-alt}}}}}

\textbf{Master of Science;\texttt{*}} \let\thefootnote\relax\footnote{* Official statement of comparability to EU equivalent degree available, issued by \href{https://www.upol.cz/en/}{\textsc{Palacký University Olomouc}}, Czech Republic.}\hfill {University of Tehran}\\
Thesis Title: A study on the role of LTBP-1 in human trabecular meshwork cells.\hfill {2011 -- 2014}
 
\textbf{Bachelor of Science;}  \hfill{University of Tehran}\\
 Thesis Title: Genetic delimitation of \href{https://onlinelibrary.wiley.com/doi/abs/10.1111/boj.12015}{\textit{Amaranthaceae} and \textit{Plumbaginaceae}} populations.\hfill {2006 - 2010}
 
\end{rSection}

\begin{rSection}{Training}
\vspace{-1em}
\setstretch{1.25}
    \item High Performance Computing \hfill{IT4Innovations National Super-computing Centre}\\
          Parallel computing,  \hfill August 2023
    \item Pharmacovigilance medical writing: \hfill {Janssen Pharmaceuticals}\\
          Regulatory Systematic Review Writing, AMA Manual of Style, GVP. \hfill August 2022
    \item MDR regulatory affairs comprehensive training: \hfill  {Ethicon, Inc.}\\
          Technical Documentation, NB submission, GDP, GMP, GDPR. \hfill May 2020
\end{rSection}

\begin{rSection}{Awards}
\setstretch{1.25}
Ministry of Health of the Czech Republic \hfill January 2022\\
Grant NU22-A-105 for public health research.
\end{rSection}

\begin{rSection}{Relevant Membership} 
\setstretch{1.25}
    TEAM-PRRC (Person Responsible for Regulatory Compliance) \hfill December 2022 - Present\\
\end{rSection}

\end{document}
